Title field: summary

### 2021-01-18 inst/examples/title.Rmd
ok

 * `r length(unique(df$title))` [unique titles](output.tables/title_accepted.csv)
 * `r sum(!is.na(df$title))`/`r nrow(df)` original documents (`r round(100*mean(!is.na(df$title)), 1)`%) have data
 * `r sum(is.na(df$title))`/`r nrow(df)` documents (`r round(100*mean(is.na(df$title)), 1)`%) have missing (NA) entry
 * [Discarded titles](output.tables/title_discarded.csv) (excluding NA entries in the original data)

Top-`r ntop` titles are shown together with the number of documents.

```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
library(ggplot2)
p <- top_plot(df, "title", ntop = ntop) +
       scale_y_log10() +
       labs(y = "Entries (n)", title = "Top titles")
print(p)
```

>>>>

 * [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$title))`
 * [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/title_discarded.csv")) - 1)` 
 * Original documents with non-NA titles: `r sum(!is.na(df$title))` / `r nrow(df)` (`r round(100*mean(!is.na(df$title)), 1)`%)
 * Original documents with missing (NA) titles `r sum(is.na(df$title))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$title)), 1)`%)

Top-`r ntop` titles and their title counts.

```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
library(ggplot2)
p <- top_plot(df, "title", ntop = ntop) +
       scale_y_log10() +
       labs(y = "Entries (n)", title = "Top titles")
print(p)
```
